Assessing paravascular transport in the parenchyma by partial differential equation (PDE) constrained optimization

### 2018-10-29 tex/paper.tex
removed one ref

\newcommand{\kam}[1]{\textcolor{blue}{#1}}
\newcommand{\fixme}[1]{\textcolor{orange}{#1}}
\newcommand{\lars}[1]{\textcolor{magenta}{#1}}
\author{Lars Magnus Valnes, Sebastian K. Mitusch, Geir A. Ringstad, \\ 
Per Kristian Eide, Simon W. Funke, Kent-Andre Mardal }

@@

%The recently proposed glymphatic system propose a new mechanism for waste
%clearance from the brain and has opened for a new paradigm in        
%research on Alzheimer's disease where one of the defining features
%is that metabolic waste accumulate within the brain. The glymphatic system is still controversial and while
%experimental investigations in rodents as well as novel MRI investigations in humans
%provide evidence for the existence of this system, a proper theoretical
%foundation is currently missing from the bio-mechanical point of view. In particular,
%a crucial question in the current debate is how much the system accelerate
%waste clearance when compared to extra-cellular diffusion alone. In this paper,
%we will therefore evaluate to what extent partial differential constrained optimization methods
%can be used to identify modeling parameters for glymphatic transport when we    
%assume that the underlying equation can be represented by a diffusion equation
%representing extra-cellular diffusion and possibly dissipation caused by the glymphatic system.
\end{abstract}
\section{Introduction}
In 2012, ~\citet{iliff2012paravascular} provided evidence for a a brain-wide paravascular system, denoted the glymphatic system, which is a pathway for transport of fluids and solutes. It was proposed to have an important metabolic role by providing a pathway for clearance of waste solutes from the brain. Evidence was given that the activity of the glymphatic system increases during sleep ~\citet{xie2013sleep}, thus linking sleep to clearance of toxic substances from the brain. The glymphatic system seems to become impaired during aging, and failure of the glymphatic system may play a role in neurodegenerative disease and development of Alzheimer's disease. Evidence for a brain-wide glymphatic system in humans was first obtained in 2015 \citet{eide2015mri}, and in 2018 \citet{ringstad2018brain} provided evidence that glymphatic function is deteriorated in individuals with dementia, as compared to controls.
Several aspects of the glympahtic system are still debated, for example whether glymphatic transport of solutes is by convective mechanisms or by diffusion.

@@

The work of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
that diffusion was a governing transport mechanism in the brain and with an estimated order of magnitude $1.0\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for large molecules. This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194}, while subjects with dementia typically have higher value and variation \cite{goujon2018can}. Of course diffusion coefficients, 
measured by DTI at a time-scale of 7-30 minutes, may not be representative for the process on a
longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vascular system occupies around 3\% of the brain volume  \cite{nicholson2001diffusion},
and the paravascular network is substantially smaller potentially renders the paravascular transport  invisible at the short time-scales of a DTI acquisition while it may still be effective on longer time scales.

@@

The signal difference between observation times were adjusted in \cite{eidevalnes}. Thus we can express the change in $T_1$ due to tracer as 

@@

The tracer concentration was estimated in a preprocessing step, using the parameters obtained from the T1-map, MPRAGE MRI protocol \cite{eidevalnes} and the value for $r_1$ found in \cite{pmid16230904}. In the computation, the function \eqref{scaledmagnetization} was computed for $ T_1\in \lbrace 200, 4000 \rbrace$ creating a lookup table. The lookup table was utilized with the baseline signal increase to estimate $T_1\sp{c}$, and then the concentration was computed using \eqref{EQ::contrast}.

@@

\subsection{Diffusion tensor imaging}
In addition to the T1 and T2 weighted sequences described above we have also obtained diffusion tensor imaging to assess the apparent diffusion 
coefficients on short time-scales. Images are shown in Figure~\ref{figuredti} where the largest diffusion coefficient (shown in 
red in the middle figure) is shown to be around $1.0\mathrm{e}{-3}  \mathrm{mm^2/s}$. We remark that we have not included possible anisotropy, shown in 
the right-most image in Figure~\ref{figuredti} and that these images show the apparent diffusion coefficient for free water molecules (18 Da).      
The diffusivity of the Gadovist (600 Da) \cite{MGadobutrol} was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da) \cite{MGgDPTA}. This is due to the fact that both molecules have similar mass, and based on Stoke-Einstein equation should also have similar diffusion coefficients. The free diffusion coefficient for Gd-DPTA was estimated in \citet{GdDPTA-DIFFUSION} to be $3.8\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$.
The fractional anisotropy is defined as 
\begin{equation}
FA\sp{2} =  \frac{3}{2} \frac{ (\lambda_1 - MD )\sp{2} +(\lambda_2 - MD )\sp{2} +(\lambda_3 - MD )\sp{2}}{\lambda\sp{2}_1 + \lambda\sp{2}_2  +\lambda\sp{2}_3 },
\end{equation}
with the mean diffusivity $MD$ defined as 
\begin{equation}
MD = \frac{\lambda_1 +\lambda_2 +\lambda_3 }{3}.
\end{equation}
In these equations $\lambda_i$ denotes the eigenvalues of the diffusion tensor.
\begin{figure}
\centering
\includegraphics[width=0.80\textwidth]{DTI-zoom.png} 
\caption{The left panel show the anatomical map. The middle panel show the apparent diffusion coefficients (ADC) obtained from DTI. The right panel shows the computed fractional anisotropy (FA) from the DTI.}
\label{figuredti} 
\end{figure}

@@

The mesh construction was patient-specific and used the MRI of a patient diagnosed with idiopathic normal pressure hydrocephalus (iNPH). The software Freesurfer was used to segment and create the polyhedral surfaces of the white and grey matter. Then the T2 weighted MRI \cite{eidevalnes} was used to segment the CSF compartment surrounding the cerebral and the lateral ventricles. CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construct the mesh. The computational requirement for the resulting mesh was significant, therefore two submeshes was also constructed, see Figure~\ref{Fig::Mesh}.
\begin{figure}
\centering
\includegraphics[scale=0.2]{mesh.png} 
\caption{The leftmost image A) shows the mesh created from the baseline MR image with 3 domains, while the rightmost image  B) shows the mesh created from the baseline MR image with 2 domains. The blue domain corresponds to CSF domain, $\Omega_{CSF}$, the purple domain corresponds to grey matter,  $\Omega_{GM}$, and the white domain corresponds to white matter, $\Omega_{WM}$. }
\label{Fig::Mesh}
\end{figure}
The 3 domain mesh in Figure~\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh (without the CSF compartment) Figure~\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices. 
%The mesh coordinates (X,Y,Z) are given in $\mathrm{mm}$ \lars{ with $X \in \lbrace -70.5,-18\rbrace, Y \in \lbrace -73.5,28.8  \rbrace ,Z \in \lbrace 16.6,60.7 \rbrace$ }.

@@

\subsubsection{Comparison with results obtained from DTI analysis}

The median diffusion coefficient in the DTI was estimated to be $8.7\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ in white matter and $1.0\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ in grey matter. This corresponds to a tortuosity of $1.85$ and $1.73$, given that the self-diffusivity of water has been estimated to be around $3.0\mathrm{e}{-3}\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$. Then the reference value $3.8\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the apparent diffusion coefficient in the grey and white matter to  be $ 1.26\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$ and $1.10\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ respectively. This estimation assumes that the tortuosity is independent for molecules with mass lower than 1kDa.

@@

\section{Discussion}
The methodology presented here for identification of diffusion coefficients and boundary conditions with application to the glymphatic system appears to work quite 
well for regularization parameters varying by orders of magnitude. The regularization parameters  $\alpha \in \lbrace 1.0\mathrm{e-6}, 1.0\mathrm{e}{-2} \rbrace$, $\beta \in \lbrace 1.0\mathrm{e}{-2} , 1.0 \rbrace$ with the requirement $\alpha / \beta < 1.0\mathrm{e}{-2}$ gave a relative error of  
4.1\% in grey matter and 3.6 \% in white matter. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
in the Figures ~\ref{12hourswithnoise} and ~\ref{24hourswithnoise} with noise amplitude of 23\% of maximum value. However, the addition of noise required that $\beta = 1.0 $ to obtain consistent convergence. 
Crucial in our application is the interplay between the regularization term that regulates the smoothness of the boundary conditions as well as the integrated magnitude of the boundary conditions over time, i.e. $\alpha$ and $\beta$. Further, we observed that the importance of interplay of these parameters increases with the number of time steps. This is, however, not surprising because our observations are sparse
in time and hence an oscillating boundary condition in time will minimize the integrated boundary condition at the cost of reducing the smoothness in time. The selected range of regularization parameters showed a decrease in error with more timesteps, rather than oscillation.

While a more comprehensive study involving more patients would be required in order to assess clearance in health and disease, a few remarks here are in order. 
First of all, the process investigated here is the clearance of Gadovist from CSF into the interstitium which may differ from the clearance of metabolic waste 
from the interstitium via the CSF. That said, 
we find that the diffusion coefficients is 42-100\% larger than what was found by the DTI modality. As such, we predict that the paravascular system 
plays a significant role.  
However, we have not yet been able to assess the self-diffusion of water as well as the diffusivity of Gadovist used in this study with phantom models. As such 
the values used with \eqref{tortuosity} must be taken with caution. Furthermore,    
the computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Figure~\ref{figuredti}. It can be seen in Figure~\ref{Fig::realdata} that the region with high FA have negligible amounts of tracer present. Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can not evaluate a static environment. Thus observations of tracer in regions with anisotropy can be considered a requirement before adding anisotropy to the model.

The computational model uses 2 global controls for the diffusion coefficients, while it can be seen in  Figure~\ref{figuredti} that diffusion coefficients can be considered a spacial function. However, the implementation of control parameters for each degree of freedom would significantly increase the computational cost. Since the diffusivity appears to be regional, using region specific control parameters seems to be a better option.
It can also be taken into consideration to model the diffusion coefficients as a function in time, given the report of increased clearance in rodents during sleep \cite{xie2013sleep}. This would indicate a time-dependent diffusivity, given that the clearance in the brain is driven by diffusion. %The time-dependency would correspond to a change in tortuosity, since properties of the tracer molecule do not change.
The hypothesis of the glymphatic system \cite{iliff2012paravascular} states that the waste is cleared through the veins in the parenchyma. This gives the tracer additional pathways that is not considered in the computational model. These additional pathways can be modeled as a drainage, which can be included as a control source term.

@@

Previous studies~\cite{holter2017interstitial, smith2017glymphatic} suggest that diffusion dominates in the interstitium. Furthermore, 
~\cite{asgari2016glymphatic, brynjfm, Diem} have found that dissipation in the paravascular spaces adds less than a factor two
to diffusion for solute transportation. If we consider that the vasculature system occupy 3\% of the brain volume
%of the brain 
and that the paravascular space presumably occupy less space. Then the 42-100\% that we find here seems significant and it is difficult to explain or ignore.     
%In summary, using this model, we estimated diffusion coefficients that were 42-100\% larger than estimated by DTI acquisitions. Our results indicate that dissipation of solutes along the paravascular rout has a factor of 30, as compared to diffusion alone. However, the present study did not examine whether transport is by convective mechanisms.
%

>>>>

\newcommand{\kam}[1]{\textcolor{blue}{#1}}
\newcommand{\fixme}[1]{\textcolor{orange}{#1}}
\newcommand{\lars}[1]{\textcolor{magenta}{#1}}
\author{Lars Magnus Valnes, Sebastian K. Mitusch, Geir Ringstad, \\ 
Per Kristian Eide, Simon W. Funke, Kent-Andre Mardal }

@@

%The recently proposed glymphatic system propose a new mechanism for waste
%clearance from the brain and has opened for a new paradigm in        
%research on Alzheimer's disease where one of the defining features
%is that metabolic waste accumulate within the brain. The glymphatic system is still controversial and while
%experimental investigations in rodents as well as novel MRI investigations in humans
%provide evidence for the existence of this system, a proper theoretical
%foundation is currently missing from the bio-mechanical point of view. In particular,
%a crucial question in the current debate is how much the system accelerate
%waste clearance when compared to extra-cellular diffusion alone. In this paper,
%we will therefore evaluate to what extent partial differential constrained optimization methods
%can be used to identify modeling parameters for glymphatic transport when we    
%assume that the underlying equation can be represented by a diffusion equation
%representing extra-cellular diffusion and possibly dissipation caused by the glymphatic system.
\end{abstract}
\section{Introduction}
In 2012, ~\citet{iliff2012paravascular} provided evidence for a a brain-wide paravascular system, denoted the glymphatic system, which is a pathway for transport of fluids and solutes. It was proposed to have an important metabolic role by providing a pathway for clearance of waste solutes from the brain. Evidence was given that the activity of the glymphatic system increases during  sleep by ~\citet{xie2013sleep}, thus linking sleep to clearance of toxic substances from the brain. The glymphatic system seems to become impaired during aging, and failure of the glymphatic system may play a role in neurodegenerative disease and development of Alzheimer's disease. Evidence for a brain-wide glymphatic system in humans was first obtained in 2015 by \citet{eide2015mri}, and in 2018 \citet{ringstad2018brain} provided evidence that glymphatic function is deteriorated in individuals with dementia, as compared to controls.
Several aspects of the glympahtic system are still debated, for example whether glymphatic transport of solutes is by convective mechanisms or by diffusion.

@@

The work of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
that diffusion was a governing transport mechanism in the brain and with an estimated order of magnitude $1.0\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for large molecules. This is confirmed with diffusion tensor imaging (DTI) where young and healthy subjects have typical diffusion values in white matter around $0.7-0.9\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ \citet{Helenius194},
while subjects with dementia typically have higher value and variation \cite{goujon2018can} . Of course diffusion coefficients, 
measured by DTI at a time-scale of 7-30 minutes, may not be representative for the process on a
longer time-scale, at least if the paravascular pathway plays an important role. The fact that the vascular system occupies around 3\% of the brain volume  \cite{nicholson2001diffusion},
and the paravascular network is substantially smaller potentially renders the paravascular transport  invisible at the short time-scales of a DTI acquisition while it may still be effective on longer time scales.

@@

The signal difference between observation times were adjusted in \cite{ringstad2018brain}. Thus we can express the change in $T_1$ due to tracer as 

@@

The tracer concentration was estimated in a preprocessing step, using the parameters obtained from the T1-map, MPRAGE MRI protocol \cite{ringstad2018brain} and the value for $r_1$ found in \cite{pmid16230904}. In the computation, the function \eqref{scaledmagnetization} was computed for $ T_1\in \lbrace 200, 4000 \rbrace$ creating a lookup table. The lookup table was utilized with the baseline signal increase to estimate $T_1\sp{c}$, and then the concentration was computed using \eqref{EQ::contrast}.

@@

\subsection{Diffusion tensor imaging}
In addition to the T1 and T2 weighted sequences described above we have also obtained diffusion tensor imaging to assess the apparent diffusion 
coefficients on short time-scales. Images are shown in Figure~\ref{figuredti} where the largest diffusion coefficient (shown in 
red in the middle figure) is shown to be around $1.0\mathrm{e}{-3}  \mathrm{mm^2/s}$. We remark that we have not included possible anisotropy, shown in 
the right-most image in Figure~\ref{figuredti} and that these images show the apparent diffusion coefficient for free water molecules (18 Da).      
The diffusivity of the Gadovist (600 Da) \cite{MGadobutrol} was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da) \cite{MGgDPTA}. This is due to the fact that both molecules have similar mass, and based on Stoke-Einstein equation should also have similar diffusion coefficients. The free diffusion coefficient for Gd-DPTA was estimated in \citet{GdDPTA-DIFFUSION} to be $3.8\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$.
The fractional anisotropy is defined as 
\begin{equation}
FA\sp{2} =  \frac{3}{2} \frac{ (\lambda_1 - MD )\sp{2} +(\lambda_2 - MD )\sp{2} +(\lambda_3 - MD )\sp{2}}{\lambda\sp{2}_1 + \lambda\sp{2}_2  +\lambda\sp{2}_3 },
\end{equation}
with the mean diffusivity $MD$ defined as 
\begin{equation}
MD = \frac{\lambda_1 +\lambda_2 +\lambda_3 }{3}.
\end{equation}
In these equations $\lambda_i$ denotes the eigenvalues of the diffusion tensor.
\begin{figure}
\centering
\includegraphics[width=0.80\textwidth]{DTI-zoom.png} 
\caption{The left panel shows the anatomical map. The middle panel shows the apparent diffusion coefficients (ADC) obtained from DTI. The right panel shows the computed fractional anisotropy (FA) from the DTI.}
\label{figuredti} 
\end{figure}

@@

The mesh construction was patient-specific and used the MRI of a patient diagnosed with idiopathic normal pressure hydrocephalus (iNPH). The software Freesurfer was used to segment and create the polyhedral surfaces of the white and grey matter. Then the T2 weighted MRI \cite{ringstad2018brain} was used to segment the CSF compartment surrounding the cerebral and the lateral ventricles. CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construct the mesh. The computational requirement for the resulting mesh was significant, therefore two submeshes was also constructed, see Figure~\ref{Fig::Mesh}.
\begin{figure}
\centering
\includegraphics[scale=0.2]{mesh.png} 
\caption{The leftmost image A) shows the mesh created from the baseline MR image with 3 domains, while the rightmost image  B) shows the mesh created from the baseline MR image with 2 domains. The blue domain corresponds to CSF domain, $\Omega_{CSF}$, the purple domain corresponds to grey matter,  $\Omega_{GM}$, and the white domain corresponds to white matter, $\Omega_{WM}$. }
\label{Fig::Mesh}
\end{figure}
The 3 domain mesh in Figure~\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh (without the CSF compartment) Figure~\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices. 
%The mesh coordinates (X,Y,Z) are given in $\mathrm{mm}$ \lars{ with $X \in \lbrace -70.5,-18\rbrace, Y \in \lbrace -73.5,28.8  \rbrace ,Z \in \lbrace 16.6,60.7 \rbrace$ }.

@@

\subsubsection{Comparison with results obtained from DTI analysis}
The median diffusion coefficient in the DTI was estimated to be $8.7\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ in white matter and $1.0\mathrm{e}{-3} \mathrm{mm\sp{2}/s}$ in grey matter. This corresponds to a tortuosity of $1.85$ and $1.73$, given that the self-diffusivity of water has been estimated to be around $3.0\mathrm{e}{-3}\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$. The reference value $3.8\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ for Gd-DPTA then gives an estimate for the apparent diffusion coefficient in the grey and white matter to  be $ 1.26\mathrm{e}{-4}\mathrm{mm\sp{2}/s}$ and $1.10\mathrm{e}{-4} \mathrm{mm\sp{2}/s}$ respectively. This estimation assumes that the tortuosity is independent for molecules with mass lower than 1kDa.

@@

\section{Discussion}
The methodology presented here for identification of diffusion coefficients and boundary conditions with application to the glymphatic system appears to work quite 
well for regularization parameters varying by orders of magnitude. The regularization parameters  $\alpha \in \lbrace 1.0\mathrm{e-6}, 1.0\mathrm{e}{-2} \rbrace$, $\beta \in \lbrace 1.0\mathrm{e}{-2} , 1.0 \rbrace$ with the requirement $\alpha / \beta < 1.0\mathrm{e}{-2}$ gave a relative error of  
4.1\% in grey matter and 3.6 \% in white matter when tested against a manifactured solution. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
in the Figures \ref{12hourswithnoise} and \ref{24hourswithnoise} with noise amplitude of 23\% of maximum value. However, the addition of noise required that $\beta = 1.0 $ to obtain consistent convergence. 
Crucial in our application is the interplay between the regularization term that regulates the smoothness of the boundary conditions as well as the integrated magnitude of the boundary conditions over time, i.e. $\alpha$ and $\beta$. Further, we observed that the importance of interplay of these parameters increases with the number of time steps. This is, however, not surprising because our observations are sparse
in time and hence an oscillating boundary condition in time will minimize the integrated boundary condition at the cost of reducing the smoothness in time. The selected range of regularization parameters showed a decrease in error with more timesteps, rather than oscillation.

While a more comprehensive study involving more patients would be required in order to assess clearance in health and disease, a few remarks here are in order. 
First of all, the process investigated here is the clearance of Gadovist from CSF into the interstitium which may differ from the clearance of metabolic waste 
from the interstitium via the CSF. That said, 
we find that the diffusion coefficients is 42\% larger in grey matter and 100\% larger in white matter than what was found by the DTI modality. As such, we predict that the paravascular system 
plays a significant role.  
However, we have not yet been able to assess the self-diffusion of water as well as the diffusivity of Gadovist used in this study with phantom models. As such 
the values used with \eqref{tortuosity} must be taken with caution. Furthermore,    
the computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Figure~\ref{figuredti}. It can be seen in Figure~\ref{Fig::realdata} that the region with high FA have negligible amounts of tracer present. Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can not evaluate a static environment. Thus observations of tracer in regions with anisotropy can be considered a requirement before adding anisotropy to the model.

The computational model uses 2 global controls for the diffusion coefficients, while it can be seen in  Figure~\ref{figuredti} that diffusion coefficients can be considered a spatial function. However, the implementation of control parameters for each degree of freedom would significantly increase the computational cost and increase the demand for regularization. Since the diffusivity appears to be regional, using region specific control parameters seems to be a better option.
It can also be taken into consideration to model the diffusion coefficients as a function in time, given the report of increased clearance in rodents during sleep \cite{xie2013sleep}. This would indicate a time-dependent diffusivity, given that the clearance in the brain is driven by diffusion. %The time-dependency would correspond to a change in tortuosity, since properties of the tracer molecule do not change.
The hypothesis of the glymphatic system \cite{iliff2012paravascular} states that the waste is cleared through the veins in the parenchyma. This gives the tracer additional pathways that is not considered in the computational model. These additional pathways can be modeled as a drainage, which can be included as a control source term.

@@

Previous studies~\cite{holter2017interstitial, smith2017glymphatic} suggest that diffusion dominates in the interstitium. Furthermore, 
~\cite{asgari2016glymphatic, brynjfm, Diem} have found that dissipation in the paravascular spaces adds less than a factor two
to diffusion for solute transportation. If we consider that the vasculature system occupy 3\% of the brain volume
%of the brain 
and the paravascular space presumably occupy less space. Then the 42\% increase in grey matter and 100\% in white matter that we find here seem significant and the results point towards of the glymphatic clearance.  
%In summary, using this model, we estimated diffusion coefficients that were 42-100\% larger than estimated by DTI acquisitions. Our results indicate that dissipation of solutes along the paravascular rout has a factor of 30, as compared to diffusion alone. However, the present study did not examine whether transport is by convective mechanisms.
%
